---
title: "FA6"
author: "Kiana Marie Dizon"
date: "2024-09-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1: Quartiles of the Distribution

Explanation:

The total number of students is 120.

- Quartiles are calculated based on the cumulative student frequencies:

Q1 (25th percentile) is at the position 0.25 * 120 = 30.

Q2 (50th percentile, median) is at 0.50 * 120 = 60.

Q3 (75th percentile) is at 0.75 * 120 = 90.

```{r 1}

grades <- c(90, 80, 70, 60, 50, 40, 30)
students <- c(9, 32, 43, 21, 11, 3, 1)

#frequency table
freq_table <- data.frame(Grade = grades, Number_of_Students = students)

# Cumulative frequencies
freq_table$Cumulative_Students <- cumsum(students)


knitr::kable(freq_table, caption = "Frequency Distribution of Grades")


total_students <- sum(students)

# Quartiles calculation
Q1 <- 0.25 * total_students
Q2 <- 0.50 * total_students
Q3 <- 0.75 * total_students


Q1
Q2
Q3

```

Question 2: Absolute and Relative Dispersion
Explanation:

- Absolute Dispersion is just the standard deviation:

For Statistics: SD = 8

For Algebra: SD = 7.6

- Relative Dispersion (coefficient of variation):

For Statistics: CV= 8/78 â‰ˆ 0.1026

For Algebra: CV= 7.6/73 â‰ˆ 0.1041


```{r 2}

means <- c(78, 73)
sds <- c(8, 7.6)
subjects <- c("Statistics", "Algebra")

# Absolute dispersion is just the standard deviation
absolute_dispersion <- sds

# Relative dispersion (Coefficient of variation = standard deviation / mean)
relative_dispersion <- sds / means

#data frame 
dispersion_df <- data.frame(Subject = subjects, Mean = means, Standard_Deviation = sds, 
                            Absolute_Dispersion = absolute_dispersion, 
                            Relative_Dispersion = relative_dispersion)


knitr::kable(dispersion_df, caption = "Dispersion Comparison between Statistics and Algebra")

```

Question 3: Proving the Mean and Standard Deviation of Standard Scores

```{r 3}

data_set <- c(6, 2, 8, 7, 5)

#mean and standard deviation of the set
mean_set <- mean(data_set)
std_set <- sd(data_set)

# Convert to standard scores
standard_scores <- (data_set - mean_set) / std_set

# data frame 
standard_scores_df <- data.frame(Original_Score = data_set, Standard_Score = standard_scores)


knitr::kable(standard_scores_df, caption = "Standard Scores of the Data Set")

# Mean and standard deviation of the standard scores
mean_standard_scores <- mean(standard_scores)
std_standard_scores <- sd(standard_scores)


list(Mean_of_Standard_Scores = mean_standard_scores, SD_of_Standard_Scores = std_standard_scores)

```

Question 4: Mean and Standard Deviation of Mass

```{r 4}

masses <- c(20.48, 35.97, 62.34)
mass_sds <- c(0.21, 0.46, 0.54)


mass_df <- data.frame(Mass = masses, SD = mass_sds)


knitr::kable(mass_df, caption = "Masses and their Standard Deviations")

# Mean of the sum of masses
mean_sum_mass <- sum(masses)

# Standard deviation of the sum of masses (square root of sum of variances)
std_sum_mass <- sqrt(sum(mass_sds^2))


list(Mean_of_Sum = mean_sum_mass, SD_of_Sum = std_sum_mass)

```

Question 5: Credit Hour Distribution

- Mean (Expected value):
ð¸(ð‘‹)=6(0.1)+9(0.2)+12(0.4)+15(0.2)+18(0.1)=12

- Variance: 
Var(X)=(6âˆ’12)^2(0.1) + (9âˆ’12)^2(0.2) + (12âˆ’12)^2(0.4) + (15âˆ’12)^2(0.2) + (18âˆ’12)^2(0.1)=9

```{r 5}
#credit hour distribution
x <- c(6, 9, 12, 15, 18)
p_x <- c(0.1, 0.2, 0.4, 0.2, 0.1)


credit_df <- data.frame(Credit_Hours = x, Probability = p_x)


knitr::kable(credit_df, caption = "Credit Hour Distribution")

# Mean (Expected value) of credit hours
mean_x <- sum(x * p_x)

# Variance of credit hours
var_x <- sum((x - mean_x)^2 * p_x)

# Display results
list(Mean = mean_x, Variance = var_x)

```
